Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2018-02-02 paper.tex
25 pages version and cover letter
Added subsection about interpolants
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

% Metadata Information
\acmJournal{TCPS}
\acmVolume{9}
\acmNumber{9}
\acmArticle{99}
\acmYear{2017}
\acmMonth{12}
\copyrightyear{2017}
%\acmArticleSeq{9}

@@

% Paper history
\received{February 2007}
\received[revised]{March 2009}
\received[accepted]{June 2009}

@@

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
%\renewcommand{\baselinestretch}{0.93}

@@

Figure~\ref{intelligent-product} shows some examples of ECPSs, which typically consist of a human-machine interface ({\it e.g.}, keyboard and display), a processing unit ({\it e.g.}, real-time computer system), and an instrumentation interface ({\it e.g.}, sensor, network, and actuator) that can be connected to some physical plant~\cite{Kopetz11}. Indeed, many current ECPSs, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may cost civilian lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health and even many aspects of their lives, with serious consequences. On the one hand, portable ECPSs are capable of monitoring and identifying conditions that are very difficult for a physician, mainly when his contact with patients happens only in medical clinics. On the other hand, wrong or incomplete diagnostic data may delay necessary treatments or deteriorate patients' health. 
%
\begin{figure}[!t]
	\centering
	\includegraphics[width=\textwidth]{figure1.jpg}
	\caption{An ECPS is part of a well-specified larger one (intelligent product).}
	\label{intelligent-product}
\end{figure}

@@

%--------------------------------------
\section{Bounded Model Checking (BMC)}
\label{Preliminaries}
%--------------------------------------

Bounded Model Checking (BMC) based on SAT was originally proposed to verify hardware designs~\cite{Biere99,handbook09}. Indeed, Biere {\it et al.} were able to successfully verify large digital circuits with approximately $9510$ latches and $9499$ inputs, leading to BMC formulae with $4 \times 10^6$ variables and $1.2 \times 10^7$ clauses to be checked by standard SAT solvers. BMC based on SMT~\cite{BarrettSST09}, in turn, was originally proposed to deal with increasing software verification complexity~\cite{Armando2009}. 
%
In general, BMC techniques aim to check the violation of a given (safety) property at a given system depth, as shown in Figure~\ref{bounded-model-checking}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure2.jpg}
	\caption{Bounded Model Checking.}
	\label{bounded-model-checking}
\end{figure}

@@

As an example, consider a simple C program (slightly modified from~\cite{Strichman08}) with an exponential number of paths, as shown in Figure~\ref{figure:verification-condition}(a); the corresponding C program, in single static assignment (SSA) form~\cite{Appel97}, is shown in Figure~\ref{figure:verification-condition}(b). The SSA form is an intermediate representation, which is used by compilers to facilitate optimizations and transformations of source code. The common property in SSA form is that every variable has only one definition in the program text. This is achieved by introducing a fresh variable from the original name ({\it e.g.}, with a subscript), such that every assignment has a unique left-hand side, as shown in Figure~\ref{figure:verification-condition}(b).
%
\begin{figure}[ht]
\centering
\begin{minipage}{0.45\textwidth}
\begin{lstlisting}
#include <assert.h>
int x[N], a;
...
int main(void) {
  a=N;
  for(int i=0; i<N; i++)
    if (x[i]>1)
      a--;
  assert(a<=N);
  return 0;
}
\end{lstlisting}
\end{minipage}
\begin{center}
(a)
\end{center}
\centering
\begin{minipage}{0.45\textwidth}
\begin{lstlisting}
a1 = N
a2 = (x[0] > 1) ? a1 - 1 : a1
a3 = (x[1] > 1) ? a2 - 1 : a2
a4 = (x[2] > 1) ? a3 - 1 : a3
...
an+1 = (x[N-1] > 1) ? an - 1 : an 
\end{lstlisting}
\end{minipage}
\begin{center}
(b)
\end{center}
\caption{(a) A simple C program with a loop \textit{for}. (b) The corresponding unwound C program of (a) converted into SSA form.} 
\label{figure:verification-condition}
\end{figure}

@@

%--------------------------------------
\subsection{Induction-based Verification of C Programs}
%--------------------------------------

@@

For instance, consider the C-code fragment shown in Figure~\ref{figure:inductive-invariant}. If we consider the IEEE floating-point standard (IEEE 754)~\cite{4610935,Goldberg91whatevery}, then  the loop invariant $x>0$ holds initially and after each iteration; actually, $x$ tends to infinity after $128$ iterations. Nonetheless, this invariant is not inductive, given that $x>0$ before an initial iteration does not ensure that $x>0$ after each iteration; if we initially have $x=0.9$, then $x<0$ after the fourth iteration. As a consequence, even if invariant generation procedures successfully compute such assertions, which are indeed invariant, those must be inductive, so that \textit{k}-induction verifiers can automatically prove program correctness. In this specific example, an inductive invariant would be $x>1$, given that if $x>1$ before the initial iteration, then also $x>1$ after \textit{k} iterations.
%
\begin{figure}[h]
\centering
\begin{minipage}{0.45\textwidth}
\begin{lstlisting}
#include <assert.h>
int main(void) {
 float x=2;
 while (1) {
   x = ((2*x) - 1);
 }
 return 0;
}
\end{lstlisting}
\end{minipage}
\caption{Motivating example for inductive invariants.}
\label{figure:inductive-invariant}
\end{figure}

@@

%------------------------------------------------------
%\subsection{Craig Interpolation}
%\label{sec:CraigInterpolationInModelChecking}
%------------------------------------------------------

%Another feasible alternative to prove properties in BMC is to compute Craig interpolants for inconsistent pairs (or more generally, sets) of formulae~\cite{McMillan03,McMillan05,McMillan06,McMillan07}. This alternative approach exploits the SAT/SMT solvers' ability to produce refutations, {\it i.e.}, proofs regarding the nonexistence of counterexamples of depth less than or equal to $k$. Those proofs do not ensure whether a given property holds in the model, but they contain information about reachable states of a model.

%\begin{prf}\label{interpolants}
%\begin{definition}\label{interpolants}
%\textit{Given a pair of formulae $\left(A,B\right)$, such that $A \wedge B$ is inconsistent, and a proof by resolution for $\left(A,B\right)$, an \textit{interpolant} for $\left(A,B\right)$ is a formula $F$ with the following properties~\cite{McMillan03,McMillan05}: }

%\begin{itemize}
%	\item $A \Rightarrow F$;
%	\item $F \wedge B$ \textit{is unsatisfiable};
%	\item $F$ \textit{expressed only over the common variables (nonlogical symbols) of $A$ and $B$}.
%\end{itemize}
%\end{definition}
%\end{prf}

%As an example, consider $A = \left(x_1 \wedge x_2\right)$ and $B = \left(\neg x_2 \wedge x_3\right)$. Given that $\left(x_1 \wedge x_2\right)$ must imply $F$ (or simply that $\neg x_1 \vee \neg x_2 \vee F$ hold) and $F \wedge \neg x_2 \wedge x_3$ must be unsatisfiable, one possible interpolant for the given pair of formulae $\left(A,B\right)$ is $F = x_2$, since $x_2$ is a common part of both $A$ and $B$.

%The use of interpolants allows us to define a complete method for finite-state reachability analysis based on SAT and SMT solvers. 
%
%In order to show how BMC and interpolation can be combined, we refer to Section~\ref{Preliminaries} where we define Eq.~(\ref{bounded-model-checking-biere}) and the terms $I$, $R$, and $\phi$. Now, suppose that $Q=I$ and Eq.~(\ref{bounded-model-checking-biere}) is partitioned, so that the set of initial states $I$ and the first instance of the transition relation $R$ are in set $A$, while the remaining instances of $R$ and the property $\phi$ are in set $B$, as shown in Figure~\ref{figure:computing-image-by-interpolation} (note that $k$ is unknown).
%
%\begin{figure}[ht]
%\centering
%\includegraphics[width=\textwidth]{interpolants}
%\caption{Computing image by interpolation~\cite{McMillan03}.}
%\label{figure:computing-image-by-interpolation}
%\end{figure}

%Suppose that we use an SMT solver to prove that the $A \wedge B$ is unsatisfiable, {\it i.e.}, we use an SMT solver to conclude that there is no satisfying assignment to $A \wedge B$.\footnote{Note that if at any stage we can satisfy the property $\phi$ within $k$ steps from the initial state, then we have found a counterexample.} The internal steps performed by the SMT solvers for reaching this conclusion can be used to construct a proof of unsatisfiability $\Pi$. From this proof, we can derive an interpolant $F$ for the pair of formulae $\left(A,B\right)$, i.e., $F = interpolant\left(\Pi, A, B\right)$. According to Definition~\ref{interpolants}, $A$ must imply $F$ and since we defined $A$ to be the set of initial states and the first instance of $R$ (i.e., from Figure~\ref{figure:computing-image-by-interpolation}, $A=s_{0} \wedge s_{1}$), it follows that $F$ is \textit{true} in every state reachable from the initial state in one step. In other words, we can say that $F$ is an over-approximation of the forward image of $I$~\cite{McMillan03,McMillan05}. Also according to Definition~\ref{interpolants}, the formula $F \wedge B$ must be unsatisfiable (from Figure~\ref{figure:computing-image-by-interpolation}, $B=s_{2} \wedge s_{3} \wedge \ldots \wedge s_{k}$), which means that there is no state satisfying $F$ that can reach a final state $s_k$. After computing $F$, we then check whether $F$ implies $Q$. If $F$ implies $Q$, then no reachable state can satisfy the property $\phi$ and we can thus conclude that the property holds; however, since $F$ is an approximation, we can falsely conclude that the final state is reachable. In this case, we update $Q = F \vee Q$ and $A = F \wedge R_{0}$, increase the value of $k+1$ and check whether $A \wedge B$ is unsatisfiable. If $A \wedge B$ is satisfiable, we have found a valid counter-example (i.e., a path from the initial state to the final state); otherwise, we compute the interpolant $F = interpolant\left(\Pi, A, B\right)$ again and check whether $F$ implies $Q$. This procedure is stopped when we have found a valid counterexample or have proved that the final state is not reachable (i.e., the property holds). 
%The details of the algorithm and further information about the use of interpolants in model checking can be found in~\cite{McMillan03,McMillan05,McMillan06,McMillan07}.

@@

The correctness specification $\sigma$ provided to the program synthesizer is of the form $\exists \vec{F} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free formula typically supported by SMT solvers. The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part. The phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, this witness is a candidate solution to the full synthesis formula, which is passed to the phase {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure3.jpg}
	\caption{CounterExample Guided Inductive Synthesis (CEGIS).}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

@@

Generally, state-of-the-art verification methodologies for embedded systems (including ECPSs) generate test vectors (with constraints) and use some assertion-based verification and high-level processor models, during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure4.jpg}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

>>>>

\newtheorem{prf}{\textbf{Definition}}

% Metadata Information
%\acmJournal{TCPS}
%\acmVolume{9}
%\acmNumber{9}
%\acmArticle{99}
%\acmYear{2017}
%\acmMonth{12}
%\copyrightyear{2017}
%\acmArticleSeq{9}

@@

% Paper history
\received{August 2017}
%\received[revised]{March 2009}
%\received[accepted]{June 2009}

@@

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
%\renewcommand{\baselinestretch}{0.93}
\renewcommand{\baselinestretch}{0.97}

@@

Figure~\ref{intelligent-product} shows some examples of ECPSs, which typically consist of a human-machine interface ({\it e.g.}, keyboard and display), a processing unit ({\it e.g.}, real-time computer system), and an instrumentation interface ({\it e.g.}, sensor, network, and actuator) that can be connected to some physical plant~\cite{Kopetz11}. Indeed, many current ECPSs, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may cost civilian lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health and even many aspects of their lives, with serious consequences. On the one hand, portable ECPSs are capable of monitoring and identifying conditions that are very difficult for a physician, mainly when his contact with patients happens only in medical clinics. On the other hand, wrong or incomplete diagnostic data may delay necessary treatments or deteriorate patients' health. 
%
\begin{figure}[!t]
	\centering
	\includegraphics[width=0.6\textwidth]{figure1.jpg}
	\caption{An ECPS is part of a well-specified larger one (intelligent product).}
	\label{intelligent-product}
\end{figure}

@@

%--------------------------------------
\section{SAT-based and SMT-based Verification Techniques}
\label{Preliminaries}
%--------------------------------------

%--------------------------------------
\subsection{Bounded Model Checking (BMC)}
\label{BMC}
%--------------------------------------

Bounded Model Checking (BMC) based on SAT was originally proposed to verify hardware designs~\cite{Biere99,handbook09}. Indeed, Biere {\it et al.} were able to successfully verify large digital circuits with approximately $9510$ latches and $9499$ inputs, leading to BMC formulae with $4 \times 10^6$ variables and $1.2 \times 10^7$ clauses to be checked by standard SAT solvers. BMC based on SMT~\cite{BarrettSST09}, in turn, was originally proposed to deal with increasing software verification complexity~\cite{Armando2009}. 
%
In general, BMC techniques aim to check the violation of a given (safety) property at a given system depth, as shown in Figure~\ref{bounded-model-checking}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.6\textwidth]{figure2.jpg}
	\caption{Bounded Model Checking.}
	\label{bounded-model-checking}
\end{figure}

@@

As an example, consider a simple C program (slightly modified from~\cite{Strichman08}) with an exponential number of paths, as shown in Figure~\ref{figure:verification-condition}(a); the corresponding C program, in single static assignment (SSA) form~\cite{Appel97}, is shown in Figure~\ref{figure:verification-condition}(b). The SSA form is an intermediate representation, which is used by compilers to facilitate optimizations and transformations of source code. The common property in SSA form is that every variable has only one definition in the program text. This is achieved by introducing a fresh variable from the original name ({\it e.g.}, with a subscript), such that every assignment has a unique left-hand side, as shown in Figure~\ref{figure:verification-condition}(b).
%
\begin{figure}[ht]
\centering
\begin{minipage}{0.4\textwidth}
\begin{lstlisting}[basicstyle=\footnotesize]
#include <assert.h>
int x[N], a;
...
int main(void) {
  a=N;
  for(int i=0; i<N; i++)
    if (x[i]>1)
      a--;
  assert(a<=N);
  return 0;
}
\end{lstlisting}
\end{minipage}
\begin{center}
(a)
\end{center}
\centering
\begin{minipage}{0.4\textwidth}
\begin{lstlisting}[basicstyle=\footnotesize]
a1 = N
a2 = (x[0] > 1) ? a1 - 1 : a1
a3 = (x[1] > 1) ? a2 - 1 : a2
a4 = (x[2] > 1) ? a3 - 1 : a3
...
an+1 = (x[N-1] > 1) ? an - 1 : an 
\end{lstlisting}
\end{minipage}
\begin{center}
(b)
\end{center}
\caption{(a) A simple C program with a loop \textit{for}. (b) The corresponding unwound C program of (a) converted into SSA form.} 
\label{figure:verification-condition}
\end{figure}

@@

%--------------------------------------
\subsection{Completeness}
\label{completeness}
%--------------------------------------

\textcolor{blue}{BMC can be used to find property violations up to the bound $k$ but not to prove properties, unless an upper bound is known on the depth of the state space, which is not generally the case. For software verification and synhtesis, we can adopt two different strategies in order to \emph{prove} properties: \textit{(i)} compute the \textit{completeness threshold}, which can be smaller than or equal to the maximum number of loop-iterations occurring in the program or \textit{(ii)} determine the high-level worst-case execution time (WCET), which also gives a bound on the maximum number of loop-iterations~\cite{handbook09,ckso04,Ganai08}. However, in practice, complex software systems involve large data-paths and complex expressions. Therefore, the verification conditions that arise from BMC of programs become harder to solve and require substantial amounts of memory to build.}

%--------------------------------------
\subsubsection{Induction-based Verification of C Programs}
%--------------------------------------

@@

For instance, consider the C-code fragment shown in Figure~\ref{figure:inductive-invariant}. If we consider the IEEE floating-point standard (IEEE 754)~\cite{4610935,Goldberg91whatevery}, then  the loop invariant $x>0$ holds initially and after each iteration; actually, $x$ tends to infinity after $128$ iterations. Nonetheless, this invariant is not inductive, given that $x>0$ before an initial iteration does not ensure that $x>0$ after each iteration; if we initially have $x=0.9$, then $x<0$ after the fourth iteration. As a consequence, even if invariant generation procedures successfully compute such assertions, which are indeed invariant, those must be inductive, so that \textit{k}-induction verifiers can automatically prove program correctness. In this specific example, an inductive invariant would be $x>1$, given that if $x>1$ before the initial iteration, then also $x>1$ after \textit{k} iterations.
%
\begin{figure}[h]
\centering
\begin{minipage}{0.45\textwidth}
\begin{lstlisting}[basicstyle=\footnotesize]
#include <assert.h>
int main(void) {
 float x=2;
 while (1) {
   x = ((2*x) - 1);
 }
 return 0;
}
\end{lstlisting}
\end{minipage}
\caption{Motivating example for inductive invariants.}
\label{figure:inductive-invariant}
\end{figure}

@@

%------------------------------------------------------
\subsubsection{Craig Interpolation}
\label{sec:CraigInterpolationInModelChecking}
%------------------------------------------------------

\textcolor{blue}{Another feasible alternative to prove properties in BMC is to compute Craig interpolants for inconsistent pairs (or more generally, sets) of formulae~\cite{McMillan03,McMillan05,McMillan06,McMillan07}. This alternative approach exploits the SAT/SMT solvers' ability to produce refutations, {\it i.e.}, proofs regarding the nonexistence of counterexamples of depth less than or equal to $k$. Those proofs do not ensure whether a given property holds in the model, but they contain information about reachable states of a model.}

\begin{prf}\label{interpolants}
\begin{definition}\label{interpolants}
\textit{\textcolor{blue}{Given a pair of formulae $\left(A,B\right)$, such that $A \wedge B$ is inconsistent, and a proof by resolution for $\left(A,B\right)$, an \textit{interpolant} for $\left(A,B\right)$ is a formula $F$ with the following properties}~\cite{McMillan03,McMillan05}: }

\begin{itemize}
	\item $A \Rightarrow F$;
	\item $F \wedge B$ \textit{is unsatisfiable};
	\item $F$ \textit{expressed only over the common variables (nonlogical symbols) of $A$ and $B$}.
\end{itemize}
\end{definition}
\end{prf}

\textcolor{blue}{As an example, consider $A = \left(x_1 \wedge x_2\right)$ and $B = \left(\neg x_2 \wedge x_3\right)$. Given that $\left(x_1 \wedge x_2\right)$ must imply $F$ (or simply that $\neg x_1 \vee \neg x_2 \vee F$ hold) and $F \wedge \neg x_2 \wedge x_3$ must be unsatisfiable, one possible interpolant for the given pair of formulae $\left(A,B\right)$ is $F = x_2$, since $x_2$ is a common part of both $A$ and $B$.}

\textcolor{blue}{The use of interpolants allows us to define a complete method for finite-state reachability analysis based on SAT and SMT solvers.}
%
\textcolor{blue}{In order to show how BMC and interpolation can be combined, we refer to Section~\ref{Preliminaries} where we define Eq.~(\ref{bounded-model-checking-biere}) and the terms $I$, $R$, and $\phi$. Now, suppose that $Q=I$ and Eq.~(\ref{bounded-model-checking-biere}) is partitioned, so that the set of initial states $I$ and the first instance of the transition relation $R$ are in set $A$, while the remaining instances of $R$ and the property $\phi$ are in set $B$, as shown in Figure~\ref{figure:computing-image-by-interpolation} (note that $k$ is unknown).}
%
\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{interpolants}
\caption{Computing image by interpolation~\cite{McMillan03}.}
\label{figure:computing-image-by-interpolation}
\end{figure}

\textcolor{blue}{Suppose that we use an SMT solver to prove that the $A \wedge B$ is unsatisfiable, {\it i.e.}, we use an SMT solver to conclude that there is no satisfying assignment to $A \wedge B$.\footnote{Note that if at any stage we can satisfy the property $\phi$ within $k$ steps from the initial state, then we have found a counterexample.} The internal steps performed by the SMT solvers for reaching this conclusion can be used to construct a proof of unsatisfiability $\Pi$. From this proof, we can derive an interpolant $F$ for the pair of formulae $\left(A,B\right)$, i.e., $F = interpolant\left(\Pi, A, B\right)$. According to Definition~\ref{interpolants}, $A$ must imply $F$ and since we defined $A$ to be the set of initial states and the first instance of $R$ (i.e., from Figure~\ref{figure:computing-image-by-interpolation}, $A=s_{0} \wedge s_{1}$), it follows that $F$ is \textit{true} in every state reachable from the initial state in one step. In other words, we can say that $F$ is an over-approximation of the forward image of $I$~\cite{McMillan03,McMillan05}. Also according to Definition~\ref{interpolants}, the formula $F \wedge B$ must be unsatisfiable (from Figure~\ref{figure:computing-image-by-interpolation}, $B=s_{2} \wedge s_{3} \wedge \ldots \wedge s_{k}$), which means that there is no state satisfying $F$ that can reach a final state $s_k$. After computing $F$, we then check whether $F$ implies $Q$. If $F$ implies $Q$, then no reachable state can satisfy the property $\phi$ and we can thus conclude that the property holds; however, since $F$ is an approximation, we can falsely conclude that the final state is reachable. In this case, we update $Q = F \vee Q$ and $A = F \wedge R_{0}$, increase the value of $k+1$ and check whether $A \wedge B$ is unsatisfiable. If $A \wedge B$ is satisfiable, we have found a valid counter-example (i.e., a path from the initial state to the final state); otherwise, we compute the interpolant $F = interpolant\left(\Pi, A, B\right)$ again and check whether $F$ implies $Q$. This procedure is stopped when we have found a valid counterexample or have proved that the final state is not reachable (i.e., the property holds). The details of the algorithm and further information about the use of interpolants in model checking can be found in~\cite{McMillan03,McMillan05,McMillan06,McMillan07}}.

@@

The correctness specification $\sigma$ provided to the program synthesizer is of the form $\exists \vec{F} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free formula typically supported by SMT solvers. The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part. The phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, this witness is a candidate solution to the full synthesis formula, which is passed to the phase {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{figure3.jpg}
	\caption{CounterExample Guided Inductive Synthesis (CEGIS).}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

@@

Generally, state-of-the-art verification methodologies for embedded systems (including ECPSs) generate test vectors (with constraints) and use some assertion-based verification and high-level processor models, during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{figure4.jpg}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}
